Generate data for NOBA cod ensemble modeling

### 2020-03-27 NOBAcod.Rmd
now need fishery setup files

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r, code = readLines("NOBA2Config.R")}
```

@@

```{r, code = readLines("omdimensions.R")}
```

@@

```{r, code = readLines("codsurvey.R")}
```

@@

```{r, code = readLines("codfishery.R")}
```

@@

library(here)
library(tidyverse)
library(atlantisom)

@@

Catch file contains "IsFished" species discard at age and catch at age by fishery.

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(here)
```

@@

```{r, code = readLines("./config/NOBA2Config.R"), eval=F}
```

@@

```{r, code = readLines("./config/omdimensions.R"), eval=F}
```

@@

```{r, code = readLines("./config/codsurvey.R"), eval=F}
```

@@

```{r, code = readLines("./config/codfishery.R"), eval=F}
```

@@

#library(here) now above
library(tidyverse)
library(atlantisom)

@@

Catch file contains "IsFished" species discard at age and catch at age by fishery in numbers. So now modifying load_nc_annage to get the fishery specific outputs, which requires additional atlantis fishery setup files and additions to the config files above.
